Analyse de données de composition et identification des altérations géochimiques des matériaux céramiques : le cas des productions d'un atelier ibérique (Teruel, Espagne ; II^e^-I^er^ siècles avant J.-C.)

### 2021-05-10 README.Rmd
Remove packrat

[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.2613512.svg)](https://doi.org/10.5281/zenodo.2613512)
[![GitHub Release](https://img.shields.io/github/release/nfrerebeau/TaphoCeram.svg)](https://github.com/nfrerebeau/TaphoCeram/releases)
[![Travis-CI Build Status](https://travis-ci.org/nfrerebeau/TaphoCeram.svg?branch=master)](https://travis-ci.org/nfrerebeau/TaphoCeram)

@@

> Frerebeau, N., Ben Amara, A. et Cantin, N. (2020). `r title_fr`. _Archéosciences, revue d'Archéométrie_, X, p. X-X. DOI : <https://doi.org/xxx/xxx>.

@@

**Text and figures:** [CC-BY-SA-4.0](http://creativecommons.org/licenses/by-sa/4.0/).

@@

**Datasets:** [CC-BY-SA-4.0](http://creativecommons.org/licenses/by-sa/4.0/).

@@

The original manuscript was produced with R 3.6.3. See the [DESCRIPTION](DESCRIPTION) file for a full list of the packages that this project depends on, including the suggested packages. The `packrat/` directory contains the source code for all the packages we depend on. If all works well, these will be installed on your machine when you open `TaphoCeram.Rproj` in RStudio.

>>>>

[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.2613512.svg)](https://doi.org/10.5281/zenodo.2613512)
[![GitHub Release](https://img.shields.io/github/release/nfrerebeau/TaphoCeram.svg)](https://github.com/nfrerebeau/TaphoCeram/releases)

@@

> Frerebeau, N., Ben Amara, A. et Cantin, N. (2020). `r title_fr`. _Archéosciences, revue d'Archéométrie_, 44(1), p. 33-50. DOI : <https://doi.org/10.4000/archeosciences.7220>.

@@

**Text and figures:** [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/).

@@

**Datasets:** [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/).

@@

The original manuscript was produced with R 3.6.3. See the [DESCRIPTION](DESCRIPTION) file for a full list of the packages that this project depends on, including the suggested packages.

### 2021-05-10 analysis/paper/paper.Rmd
Remove packrat

| **Version** | **Date**   | **Description**            | **DOI** |
|------------:|-----------:|:---------------------------|:--------|
| 1.0         | 2019-03-26 | Soumis à _ArchéoSciences_  | [10.5281/zenodo.2613513](https://doi.org/10.5281/zenodo.2613513) |
| 1.1         | 2019-10-15 | Corrections typographiques | [10.5281/zenodo.3490469](https://doi.org/10.5281/zenodo.3490469) |
| 1.2         | 2020-04-26 | Corrections après relecture | [10.5281/zenodo.3766901](https://doi.org/10.5281/zenodo.3766901) |
| 1.3         | 2020-06-22 | Version acceptée pour publication |  |

>>>>

| **Version** | **Date**   | **Description**            | **DOI** |
|------------:|-----------:|:---------------------------|:--------|
| 1.0         | 2019-03-26 | Soumis à _ArchéoSciences_  | [10.5281/zenodo.2613513](https://doi.org/10.5281/zenodo.2613513) |
| 1.1         | 2019-10-15 | Corrections typographiques | [10.5281/zenodo.3490469](https://doi.org/10.5281/zenodo.3490469) |
| 1.2         | 2020-04-26 | Corrections après relecture | [10.5281/zenodo.3766901](https://doi.org/10.5281/zenodo.3766901) |
| 1.3         | 2020-06-22 | Version acceptée pour publication | [10.5281/zenodo.3906262](https://doi.org/10.5281/zenodo.3906262) |
